Rapid evolution of a conspicuous dynamic visual signal in an introduced chameleon

### 2021-08-15 ms.Rmd
Fixed last bits. When removing pop_back. Need to remove code in L577.

    # Fit the main effect model
          DispBgrdCC <- lmer(dS ~ Population  + Background_pop  + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC)

@@

        Population_CC_Disp <- Wald_test(DispBgrdCC, constraints = constrain_zero(2), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

>>>>

    # Fit the main effect model
          DispBgrdCC <- lmer(dS ~ sc_svl + Background_pop  + (1|ID), data=DisplayBgrd)
          summary(DispBgrdCC)

@@

        svl_CC_Disp <- Wald_test(DispBgrdCC, constraints = constrain_zero(2), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")
